Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-06-07 PAPER.tex
syntax edits to 2.1.3

The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominated eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal. More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss. Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.

@@

% JEA - Death to eigenspectra!
%The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}. 
With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
\begin{equation}
\label{eq:converge}
\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\widehat{C}_{ij} - {C}_{ij})^2}{\sum_{ij} {C}_{ij}^2}},
\end{equation}
where $\C$ is the true covariance matrix. To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average. We then compare this to the ``true' covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations. As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors). With more independent time samples (i.e. more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.

>>>>

The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominated eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal. More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}), which leads to loss. Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.

@@

% JEA - Death to eigenspectra!
%The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}. 
With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data. We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
\begin{equation}
\label{eq:converge}
\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\widehat{C}_{ij} - {C}_{ij})^2}{\sum_{ij} {C}_{ij}^2}},
\end{equation}
where $\C$ is the true covariance matrix. To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average. We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations. As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors). With more independent time samples (i.e. more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
